---
title: "Safety Research"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
library(here)
```

</br>
</br>


Table of Contents:
==================
</br>
</br>

## Analysis By Type:
| ID         	| Year 	| Month 	| Topics                                  	                  | Software 	      | Presentation links                                                                 	|
|------------	|------	|-------	|-----------------------------------------------------------	|---------------	|------------------------------------------------------------------------------------	|
| CRSH-UNIV 	| 2020 	| NOV   	| Univariate Analysis of crash injury severity and variables 	| R   	      | |




</br>
</br>

## Weekly Meeting Updates:

| ID         	| Year 	| Month 	| Topics                                  	| Software 	| Presentation links                                                                 	|
|------------	|------	|-------	|-----------------------------------------	|----------	|------------------------------------------------------------------------------------	|
| 2020-11-01 	| 2020 	| NOV   	| Primary analysis of Binary Logit Models 	| NLOGIT   	| [Click Here](./year_2020/month/nov/wk45_nov_3/03-exploratory_analysis_truck.html) 	|
| 2020-11-02 	| 2020 	| NOV   	| Truck vs. non-truck Binary Logit Models 	| R        	| [Click Here](./year_2020/month/nov/wk46_nov_13/wk_46-updated_logit_models_2.html)   |
| 2020-11-03 	| 2020 	| NOV   	|                                         	|          	|                                                                                    	|
| 2020-11-04 	| 2020 	| NOV   	|                                         	|          	|                                                                                    	|



```{r}
library(DiagrammeR)

mermaid('
   graph LR

   DT[Datasets] --- T[Truck]
   DT[Datasets] --- NT
   T[Truck] --- T-BLM[Truck Binary Logit]
   T-BLM[Truck Binary Logit] --- T-ALL-YR[Truck All years]
   T-BLM[Truck Binary Logit] --- T-BY-YR[Truck]
   T[Truck] --- T-RPBLM[Truck Random Param Binary Logit]
   T-RPBLM[Truck Random Param Binary Logit] --- T-RAN-ALL-YR[Truck Random Param  All years]
   T-RPBLM[Truck Random Param Binary Logit] --- T-RAN-BY-YR[Truck Random Param By year ]\
   NT[NTruck] --- NT-BLM[NTruck Binary Logit]
   NT-BLM[NTruck Binary Logit] --- NT-ALL-YR[NTruck All years]
   NT-BLM[NTruck Binary Logit] --- NT-BY-YR[NTruck]
   NT[NTruck] --- NT-RPBLM[NTruck Random Param Binary Logit]
   NT-RPBLM[NTruck Random Param Binary Logit] --- NT-RAN-ALL-YR[NTruck Random Param  All years]
   NT-RPBLM[NTruck Random Param Binary Logit] --- NT-RAN-BY-YR[NTruck Random Param By year ]

   ', height = 800)

```