---
title: "Safety Research"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
library(here)
```

</br>
</br>


Table of Contents:
==================
</br>
</br>

## Analysis By Type:
| ID         	| Year 	| Month 	| Topics                                  	                  | Software 	      | Presentation links                                                                 	|
|------------	|------	|-------	|-----------------------------------------------------------	|---------------	|------------------------------------------------------------------------------------	|
| CRSH-UNIV 	| 2020 	| NOV   	| Univariate Analysis of crash injury severity and variables 	| R   	      | |


</br>
</br>

## Weekly Meeting Updates:

| ID         	| Year 	| Month 	| Topics                                  	| Software 	| Presentation links                                                                 	|
|------------	|------	|-------	|-----------------------------------------	|----------	|------------------------------------------------------------------------------------	|
| 2020-11-01 	| 2020 	| NOV   	| Primary analysis of Binary Logit Models 	| NLOGIT   	| [Click Here](./year_2020/month/nov/wk45_nov_3/03-exploratory_analysis_truck.html) 	|
| 2020-11-02 	| 2020 	| NOV   	| Truck vs. non-truck Binary Logit Models 	| R        	| [Click Here](./year_2020/month/nov/wk46_nov_13/wk_46-updated_logit_models.html)    	|
| 2020-11-03 	| 2020 	| NOV   	|                                         	|          	|                                                                                    	|
| 2020-11-04 	| 2020 	| NOV   	|                                         	|          	|                                                                                    	|
